\section{Referencias}

\begin{enumerate}
    \item Lombroso, C. (1876). \textit{L'Uomo Delinquente}. Hoepli.
    \item Goring, C. (1913). \textit{The English Convict: A Statistical Study}. His Majesty's Stationery Office.
    \item Simonyan, K., \& Zisserman, A. (2015). \textit{Very deep convolutional networks for large-scale image recognition}. In International Conference on Learning Representations (ICLR).
    \item He, K., Zhang, X., Ren, S., \& Sun, J. (2016). \textit{Deep residual learning for image recognition}. In Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition (CVPR) (pp. 770-778).
    \item Zhang, K., Zhang, Z., Li, Z., \& Qiao, Y. (2016). \textit{Joint face detection and alignment using multitask cascaded convolutional networks}. IEEE Signal Processing Letters, 23(10), 1499-1503.
    \item Selvaraju, R. R., et al. (2017). \textit{Grad-CAM: Visual Explanations from Deep Networks via Gradient-based Localization}. In Proceedings of the IEEE International Conference on Computer Vision (ICCV) (pp. 618-626).
    \item Kranthi Kumar, K., et al. (2021). \textit{Criminal face identification system using deep learning algorithm multi-task cascade neural network (MTCNN)}. Materials Today: Proceedings.
    \item Álvarez Navarro, A., et al. (2022). \textit{Revisión de los métodos de reconocimiento facial en imágenes RGB-D}. Revista Cubana de Ciencias Informáticas.
    \item Fructuoso Freire Montero, A. (2022). \textit{El reconocimiento facial como instrumento de investigación y prevención del delito}. Anuario da Facultade de Dereito da Universidade da Coruña.
    \item Garcia Silva, C. E., \& Mazon Loaiza, J. D. (2024). \textit{El reconocimiento facial y su impacto en la seguridad ciudadana: Una revisión sistemática}. Anatomía Digital, 7(1.2), 6-21.
    \item Rani, R., et al. (2025). \textit{Face Recognition System for Criminal Identification in CCTV Footage Using Keras and OpenCV}. Ingénierie des Systèmes d'Information.
\end{enumerate}